MSOA Industrial Electricty and Gas maps

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Fixed one error!

```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019) +
  geom_sf(aes(fill=" Mean consumption (kWh per meter)"))+ 
  scale_fill_continuous(name="Change in mean electricty consumption for the industrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
msoa_ndgas <- readr::read_csv(inFile)
head(msoa_ndgas)
```

@@

####Mapping the difference in non domestic gas from 2010 to 2019 
```{r Creating the difference in non domestic gas consumption in the MSOA}
msoa_2010_ndgas<-readr::read_csv(paste0(dataFolder,"/energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2010.csv"))
msoa_2019_ndgas<-readr::read_csv(paste0(dataFolder,"energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv"))
msoa_2010_ndgas$ndgas2010<-msoa_2010_ndgas$'Mean consumption (kWh per meter)'
msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'

merged_ndgas20102019<-merge(msoa_2010_ndgas, msoa_2019_ndgas, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndgas20102019)
merged_ndgas20102019$ndgas_diff<-merged_ndgas20102019$nondomgas2019 - merged_nd20102019$nondomgas2010 ##BROKEN
summary(merged_nondomgas20102019)
```

```{r Mapping the change in non domestic gas usage in the MSOA}
merged_nondomgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_nondomgas20102019 <- merge(msoa_sf_data, merged_nondomgas20102019) #merging these
ggplot2::ggplot(msoa_nondomgas20102019) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
##BROKEN
```

>>>>

```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")
```
```{r Mapping the percentage change in mean electricty consumption from the industrial sector MOSA}
merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff/ndelec2010))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")##Why does this look like this? Increased efficiency? Businesses closing down?
```
### Mapping Gas
####2019
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
msoa_ndgas <- readr::read_csv(inFile)
head(msoa_ndgas)
```

@@

####Mapping the difference in non domestic gas from 2010 to 2019 
```{r Creating the difference in non domestic gas consumption in the MSOA}
msoa_2010_ndgas<-readr::read_csv(paste0(dataFolder,"/energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2010.csv"))
msoa_2019_ndgas<-readr::read_csv(paste0(dataFolder,"energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv"))
msoa_2010_ndgas$ndgas2010<-msoa_2010_ndgas$'Mean consumption (kWh per meter)'
msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'
merged_ndgas20102019<-merge(msoa_2010_ndgas, msoa_2019_ndgas, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_ndgas20102019)
merged_ndgas20102019$ndgas_diff<-merged_ndgas20102019$nondomgas2019 - merged_nd20102019$nondomgas2010 ##BROKEN
summary(merged_nondomgas20102019)
```

```{r Mapping the change in non domestic gas usage in the MSOA}
merged_nondomgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_nondomgas20102019 <- merge(msoa_sf_data, merged_nondomgas20102019) #merging these
ggplot2::ggplot(msoa_nondomgas20102019) +
  geom_sf(aes(fill=ndgas_diff))+ 
  scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
##BROKEN
```
